Gamification Effectiveness on Education

### 2024-04-14 paper/paper.qmd
worked on the first few paragraphs of the data section

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

# Appendix {-}

@@

# References
---
nocite: '@*'
---

>>>>

The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control, Educational game, Gamification Plugin, Social networking website, Social gamified networking website. The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with hybrid learning. This course is an introduction to basic computing concepts such as word processing, spreadsheets, presentations and databases. There is an assignment for each of these four concepts which focus on testing practical skills. While, the final examination is cumulative and focus on testing conceptual knowledge.

Students have lecture every two weeks and must work independently rest of the work to learn then material. Supplementary learning material was provided such as videos and communication tools in learning material platform.

The control group just use what was mention above. Educational game used was called Ribbonhero offered by Microsoft as as free download to download Software, and player plays as virtual character Clippy and must overcome six challenges with increasing difficulty. Gamification plugin (fig 1) is integrated in the institutional management system where there are challenges, trophies/badges and a leader board. Social Networking website was run on a open source engine, Elgg (fig 2) and it functions very similar to social media where students can share their thoughts, make friends and discuss the material in class. Social gamified networking website use the same engine as the previous group and having similar features to Gamification plugin(fig 3). A summary of the groups features and potential benefits (fig 4). The study highlights that the educational game is not necessarily aligned with the learning goals, while the gamification used in this study was.

@@

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

# Appendix {.unnumbered}

@@

# References

---
nocite: '@*'
---
